---
title: "Data Repositories"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: false
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# What are Data Repositories?

At there best, data repositories provide two functions:

1. A method for sharing datasets, either publically or privately

1. A definitive, citable location for a dataset

These two functions are ever more important as research becomes more data-driven across every discipline, and as funders increasingly mandate Open Access not only for publications but also publication data. Already EPSRC requires that any metric or visualisation included in a publication based on work they funded must be made replicable by providing the underlying data.

This document describes a number of data repositories and how one might use them to incorporate data hosted with these services into an interactive data visualisation built with [shiny](http://shiny.rstudio.com) and a number of other tools. Examples of what is described for each repository (if possible), include:

- Reading data
- Writing data
- Caching data within a shiny app

## Selecting a Data Repository

For the purposes of this document, there are three types of data repository:

- File Sharing Repositories: Provide only the facility for sharing files between multiple devices and users
- Hosted Databases: Host databases against which SQL queries may be performed, with granular permissioning tools
- Data Repositories: Fully versioned platforms providing DOI and collaboration tools

In a future iteration of this document an interactive interface will be provided for the comparison of the different respositories.

# Data Repositories

The repositories in this section all provide at least the following functionality:

- Meta-data rich containers for research data
- DOI for individual deposits
- Controlled access, differs between service and may only apply to licensing of data

Note that all repositories detailed have at least a free tier or otherwise are entirely free at the point of use.

```{r child = 'Figshare/index.Rmd'}
```

```{r child = 'ORA-Data/index.Rmd'}
```

```{r child = 'Zenodo/index.Rmd'}
```

# Hosted Databases

The repositories in this section all provide the following functionality:

- A hosted SQL engine against which queries can be performed
- Permissioning for entire databases, potential permissioning at individual table level
- CRUD via API and/or ODBC

Note that not all hosted databases described below provide a free tier.

```{r child = 'AccessWebApp/index.Rmd'}
```

```{r child = 'Azure/index.Rmd'}
```

```{r child = 'ORDS/index.Rmd'}
```

# File Sharing Repositories

The repositories in this section all provide the following functionality:

- Ability to synchronise files simply between devices
- Controlled access, including public and private files


```{r child = 'Box/index.Rmd'}
```

```{r child = 'Dropbox/index.Rmd'}
```

```{r child = 'GoogleDrive/index.Rmd'}
```

```{r child = 'OneDrive/index.Rmd'}
```





