---
title: "OAuth"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(httr)
```


## References

- General Box Documentation: https://docs.box.com/docs
- 

It is not possible to directly link to a shared file with a free account - https://community.box.com/t5/Collaboration-and-Sharing/Direct-Linking-To-A-File/ta-p/148

## Oauth 2 Parameters

```{r}
client_id <- "m2wypo7lyldmwe7w5kooh21y65dg17b4"
client_secret <- "K5amICAOLCcUxXFm3LAVJvsKf2iizH58"
file_id <- "68041898313"
```


```{r}
box_oauth2_url <- "https://api.box.com/oauth2"
```


## Box API Template

In the first step of authorisation you need to send the user to [http://account.box.com/api](http://account.box.com/api)

```{r}
box_authorize_url <- "http://account.box.com/api"
```

This is an example call to the authorize api:

```{r}
box_example_authorize_call <- "https://account.box.com/api/oauth2/authorize?response_type=code&client_id=YOUR_CLIENT_ID&redirect_uri=YOUR_REDIRECT_URI&state=security_token%3DKnhMJatFipTAnM0nHlZA"
```

### Box Authorize Call

#### GET (Doesn't work)

Construct an authorize GET request:

```{r}
box_my_authorize_call <- paste0(
  "https://account.box.com/api/oauth2/authorize?response_type=code&client_id=",
  client_id,
#   "&redirect_uri=",
# YOUR_REDIRECT_URI,
"&state=security_token",
client_secret
)
```

Make the GET request 

```{r}
library(httr)
GET(box_my_authorize_call)
Oaut
```

#### oauth with httr

Following http://stackoverflow.com/q/19988160/1659890

```{r}
box_oauth_endpoint <-
  oauth_endpoint("requestToken", "authorize", "accessToken", base_url = "https://account.box.com/api/oauth2")

myapp <-
  oauth_app("ShinyApp", key = client_id, secret = "fefwef")

box_token <- oauth2.0_token(box_oauth_endpoint, myapp)

box_token

foo <- config(token = box_token)
```

I need to then make a post request to https://api.box.com/oauth2/token as follows:

```{r}
POST("https://api.box.com/oauth2/token", config(token = box_token))
```



Try and use the API based on Hadley's documentation:

```{r}


req <- GET("https://api.box.com/2.0/files", config(token = box_token))
req

stop_for_status(req)
content(req)

```











