---
title: "Azure Overview"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: false
    code_folding: show
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Azure Overview

Azure is a Microsoft Cloud Service.

# MySQL

Instructions for instantiating a MySQL database on Azure will be added later, currently this template simply extracts data from an existent database.

## Connecting to the Database

The following details are necessary to access the database, note that the .csv file containing the username and password is not provided in this tutorial due to security concerns.

```{r}
login_details <- read.csv(file = "azure_mysql_login.csv", stringsAsFactors = F)
database_domain <- "eu-cdbr-azure-north-e.cloudapp.net"
database_name <- "testdatabase2"
```

Connect!

```{r}
login_details$username
login_details$password

library(RMySQL)
azure_connection <- dbConnect(
  RMySQL::MySQL(),
  dbname = database_name,
  host = database_domain,
  username = login_details$username,
  password = login_details$password,
  port = 3306
  )

RMySQL::dbGetInfo(azure_connection)
```

List tables:

```{r}
dbListTables(azure_connection)
```

Read tables

```{r}
dbReadTable(azure_connection, "new_table")
```

## Update Database

Example Query: http://www.w3schools.com/sql/sql_update.asp

```{r}
UPDATE Customers
SET ContactName='Alfred Schmidt', City='Hamburg'
WHERE CustomerName='Alfreds Futterkiste';
```

My query:

```{r}
write_statement <- "UPDATE new_table
SET dateOfBirth='1987-01-01'
WHERE surname='Hadley';"

dbSendQuery(azure_connection, write_statement)
```

```{r}
foo <- "UPDATE new_table SET dateOfBirth='2010-01-01' WHERE surname='Hadley';"

dbSendQuery(azure_connection, write_statement)
```


## Disconnect Database

```{r}
dbDisconnect(azure_connection)
```

